---
title: "DataAnalysis_NatureComm"
output: html_document
date: "2024-08-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Libraries 
```{r}
library(reshape2)    
library(nlme)
library(lme4)
library(learnr)
library(tidyverse)
library(lmerTest)
library(patchwork)
#plot libraries
library(dplyr)
library(ggplot2)
library(tidyr)
```

# Data prep
```{r}
rm(list=ls())
setwd("/Users/marinefleury/Documents/UCL/1.PhD/1.p0802fmri/1_Projects/2.a.Long-term_gPPI/1.Results/")
clinical_info <- read_csv("/Users/marinefleury/Documents/UCL/1.PhD/1.p0802fmri/1_Projects/2.a.Long-term_gPPI/1.Results/2.clinical_info.csv")
demographics <- read_csv("/Users/marinefleury/Documents/UCL/1.PhD/1.p0802fmri/1_Projects/2.a.Long-term_gPPI/1.Results/demographics.csv")
```
#-----------------------------------------------
# Volumes: preop brain and Remnant Hippocampus
#-----------------------------------------------
```{r}
remnant <- read_csv("/Users/marinefleury/Desktop/PhD/1.gPPI/1.Results_gPPI/Flexible_Factorial/Revisions_NaturComm/remnant_Volume/remnantHipp_volumes.csv")
remnant$TLE_Group<-factor(remnant$TLE_Group,c(1,0),labels=c('Right_TLE','Left_TLE'))
```
#stats and Mann whitney tests
```{r}
##### HIPPOCAMPUS volume
#summary stats on remnant hippocampus volume
summary_stats <- remnant %>%
  group_by(TLE_Group) %>%
  summarise(
    count = n(),
    mean = mean(volume, na.rm = TRUE),
    sd = sd(volume, na.rm = TRUE),
    median = median(volume, na.rm = TRUE),
    IQR = IQR(volume, na.rm = TRUE)
  )
print(summary_stats)

##### HIPPOCAMPUS resection extent
#summary stats 
summary_stats <- remnant %>%
  group_by(TLE_Group) %>%
  summarise(
    count = n(),
    mean = mean(hipp_resection, na.rm = TRUE),
    sd = sd(hipp_resection, na.rm = TRUE),
    median = median(hipp_resection, na.rm = TRUE),
    IQR = IQR(hipp_resection, na.rm = TRUE)
  )
print(summary_stats)
#Mann Whitney: left vs right ATLR resection 
Mwhitney_resectHipp <- wilcox.test(remnant$hipp_resection ~ remnant$TLE_Group)
print(Mwhitney_resectHipp)

##### ATL resection extent (%)
#summary stats 
summary_stats <- remnant %>%
  group_by(TLE_Group) %>%
  summarise(
    count = n(),
    mean = mean(ATLresection, na.rm = TRUE),
    sd = sd(ATLresection, na.rm = TRUE),
    median = median(ATLresection, na.rm = TRUE),
    IQR = IQR(ATLresection, na.rm = TRUE)
  )
print(summary_stats)
#Mann Whitney: left vs right ATLR resection 
Mwhitney_ATL <- wilcox.test(remnant$ATLresection ~ remnant$TLE_Group)
print(Mwhitney_ATL)
#W = 83, p-value = 0.3164
```

#Volume remnant hipp: Linear Regressions
```{r}
##### HIPPOCAMPUS
# LIST CHANGE Linear regression
LTLE_listchange <- lm(List_change ~ volume, data = remnant, subset = TLE_Group == 'Left_TLE')
summary(LTLE_listchange)

RTLE_listchange <- lm(List_change ~ volume, data = remnant, subset = TLE_Group == "Right_TLE")
summary(RTLE_listchange)

# DESIGN CHANGE Linear regression
# Removea ny NA values (1)
clean_data <- na.omit(remnant[, c("List_change", "Design_change", "volume", "TLE_Group")])

LTLE_designchange <- lm(Design_change ~ volume, data = clean_data, subset = TLE_Group == "Left_TLE")
summary(LTLE_designchange)

RTLE_designchange <- lm(Design_change ~ volume, data = clean_data, subset = TLE_Group == "Right_TLE")
summary(RTLE_designchange)
```

#PLOT: remnant hipp volumes
```{r}
# Set the order of TLE group so that Left TLE appears first 
volume_combined <- remnant %>%
  pivot_longer(cols = c(volume_preHipp, volume_postHipp), names_to = "Variable", values_to = "Volume") %>%
  mutate(
    Variable = factor(Variable, levels = c("volume_preHipp", "volume_postHipp"), labels = c("Pre-Surgery", "Post-Surgery")),
    TLE_Group = factor(TLE_Group, levels = c("Left_TLE", "Right_TLE"), labels = c("Left ATLR", "Right ATLR"))
  )

# Calculate min and max values for each combination of Group and Variable
min_value <- volume_combined %>%
  group_by(TLE_Group, Variable) %>%
  summarise(min_value = min(Volume, na.rm = TRUE), .groups = 'drop')

max_value <- volume_combined %>%
  group_by(TLE_Group, Variable) %>%
  summarise(max_value = max(Volume, na.rm = TRUE), .groups = 'drop')

# Merge the min and max values back to volume_combined
volume_combined <- volume_combined %>%
  left_join(min_value, by = c("TLE_Group", "Variable")) %>%
  left_join(max_value, by = c("TLE_Group", "Variable"))

# Define custom colors for the plot
custom_colors <- c("Left ATLR" = c("Pre-Surgery" = "azure2", "Post-Surgery" = "darkcyan"),
                   "Right ATLR" = c("Pre-Surgery" = "bisque1", "Post-Surgery" = "deeppink4"))

# Create the plot
plot <- ggplot(volume_combined, aes(x = TLE_Group, y = Volume, fill = interaction(TLE_Group, Variable))) +
  geom_violin(position = position_dodge(width = 0.9), alpha = 0.6, size = 0) +
  stat_summary(geom = "crossbar",   # To add mean +/- se
               position = position_dodge(0.9),
               width = 0.9, alpha = 0.7) +
  geom_errorbar(aes(ymin = min_value, ymax = max_value),
                position = position_dodge(width = 0.9),
                width = 0.3,                    # Adjust the width of the whiskers
                alpha = 0.7,                    # Adjust transparency
                color = "black") +              # Add black color to whisker lines
  scale_fill_manual(values = unlist(custom_colors)) +
  labs(x = "Group", y = "Hippocampus Volume (mm³)", fill = "Time-point",
       title = "Hippocampus Volume Pre-Surgery and Post-Surgery") +
  theme_bw() +
  xlab("") +
  scale_y_continuous(limits = c(min(volume_combined$Volume, na.rm = TRUE), max(volume_combined$Volume, na.rm = TRUE)),
                     breaks = seq(floor(min(volume_combined$Volume, na.rm = TRUE)), ceiling(max(volume_combined$Volume, na.rm = TRUE)), by = 500)) +
  theme(axis.ticks.length = unit(0.1, "cm")) +
  theme(plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 17),
        axis.title.x = element_text(size = 9,  face = "bold"),
        axis.title.y = element_text(size = 9),
        axis.text = element_text(size = 9),
        text = element_text(size = 7),
        legend.position = "right")
print(plot)
```


# ---------------------------------------------------------------
## mixed effect models: Group*Time interaction on Memory recovery
# ---------------------------------------------------------------

```{r}
#install.packages("lme4")
#install.packages("car")
library(lme4)
library(car)
```
# LIST: mixed effect
```{r}
#convert to long format
demographics_long <- demographics %>%
  pivot_longer(
    cols = starts_with("List_1"),
    names_to = "Time",
    values_to = "Memory_Score"
  ) %>%
  mutate(
    Time = factor(Time, levels = c("List_1y", "List_10y")),
    Group = factor(Group, levels = c(0, 1, 2), labels = c("LTLE", "RTLE", "NC")),
    ID = as.factor(ID)
  )
#set NC as baseline group for comparisons in ANOVA
demographics_long$Group <- relevel(demographics_long$Group, ref = "NC")

#mixed effect model:random intercept (random effect for subjects) + main effects of group and time and interaction of group*time
mixed_model_list <- lmer(Memory_Score ~ Group * Time + (1 | ID), data = demographics_long)
summary_mixed_model <- summary(mixed_model_list)
# Apply corrections on p-values
p_values <- summary_mixed_model$coefficients[, "Pr(>|t|)"]
p_values_corrected_bh <- p.adjust(p_values, method = "BH")
# Display the corrected p-values
corrected_results <- data.frame(
    Estimate = summary_mixed_model$coefficients[, "Estimate"],
    Std_Error = summary_mixed_model$coefficients[, "Std. Error"],
    df = summary_mixed_model$coefficients[, "df"],
    t_value = summary_mixed_model$coefficients[, "t value"],
    p_value = summary_mixed_model$coefficients[, "Pr(>|t|)"],
    p_value_corrected_bh = p_values_corrected_bh
)
print(corrected_results)
#95% confidence intervals
confint(mixed_model_list,level = 0.95)
```

#DESIGN: mixed effect
```{r}
#convert to long format: DESIGN, handles with NA
demographics_long_design <- demographics %>%
  pivot_longer(
    cols = starts_with("Design_1"),
    names_to = "Time",
    values_to = "Memory_Score"
  ) %>%
  mutate(
    Time = factor(Time, levels = c("Design_1y", "Design_10y")),
    Group = factor(Group, levels = c(0, 1, 2), labels = c("LTLE", "RTLE", "NC")),
    ID = as.factor(ID)
  )
#set NC as baseline group for comparisons in ANOVA
demographics_long_design$Group <- relevel(demographics_long_design$Group, ref = "NC")
# Remove rows with missing Memory_Score
demographics_long_design <- demographics_long_design %>%
  drop_na(Memory_Score)

#mixed effect model:
mixed_model_design <- lmer(Memory_Score ~ Group * Time + (1 | ID), data = demographics_long_design)
summary(mixed_model_design)
summary_mixed_model <- summary(mixed_model_design)
p_values <- summary_mixed_model$coefficients[, "Pr(>|t|)"]
# Apply corrections
p_values_corrected_bh <- p.adjust(p_values, method = "BH")
corrected_results <- data.frame(
    Estimate = summary_mixed_model$coefficients[, "Estimate"],
    Std_Error = summary_mixed_model$coefficients[, "Std. Error"],
    df = summary_mixed_model$coefficients[, "df"],
    t_value = summary_mixed_model$coefficients[, "t value"],
    p_value = summary_mixed_model$coefficients[, "Pr(>|t|)"],
    p_value_corrected_bh = p_values_corrected_bh
)
print(corrected_results)
# 95% confidence intervals
confint(mixed_model_design,level = 0.95)
```

#--------------------------------------
# Group differences in memory outcomes
#--------------------------------------
# Data prep
```{r}
# 1. dummy variables
clinical_info$Gender <- factor(clinical_info$Gender, c(1,2), labels = c('male','female'))
clinical_info$pathology <- factor(clinical_info$pathology, c(1,2,3,4), labels = c('HS','tumour','cavernoma','gliosis'))
clinical_info$HS<-factor(clinical_info$HS,c(1,0),labels=c('HS','no_HS'))
clinical_info$ILAE_1y <- ifelse(clinical_info$ILAE_1y == 1, 1, 0) #anything that is not 1 is coded as 0
clinical_info$ILAE_10y <- ifelse(clinical_info$ILAE_10y == 1, 1, 0) #anything that is not 1 is coded as 0
clinical_info$ASM_nbr<-factor(clinical_info$ASM_nbr,c(0,1),labels=c('off','on'))
clinical_info$Seizure_Profile<-factor(clinical_info$Seizure_Profile,c(0,1),labels=c('no_sz','ongoing_sz'))

# 2.Change format to long
# Pivot longer + binarise new column Time
  # if want to remove a column: subset(select=-column)
long_clinical_outcome_list <- pivot_longer(clinical_info, cols = c(List_1y, List_10y), names_to = "Time_List", values_to = "List_scores") %>%
    view()
long_clinical_outcome_design <-  pivot_longer(clinical_info, cols = c(Design_1y, Design_10y), names_to = "Time_Design", values_to = "Design_scores") %>% 
  view()

# 3. Left TLE and right TLE separate: LTLE/RTLE patients in group 0/1
LeftTLE <- subset(clinical_info, TLE_Group == 0)
RightTLE <- subset(clinical_info, TLE_Group == 1)
Long_LeftTLE_list <- subset(long_clinical_outcome_list, TLE_Group == 0)
Long_LeftTLE_design <- subset(long_clinical_outcome_design, TLE_Group == 0)
Long_RightTLE_list <- subset(long_clinical_outcome_list, TLE_Group == 1)
Long_RightTLE_design <- subset(long_clinical_outcome_design, TLE_Group == 1)

# Filter out NA values
clinical_info_filtered <- clinical_info %>%
  filter(!is.na(Design_change))
```
# Summary statistics: ASM 
```{r}
##List recovery according to ASM
summary_stats <- clinical_info %>%
  group_by(ASM_nbr) %>%
  summarise(
    count = n(),
    mean = mean(List_change, na.rm = TRUE),
    sd = sd(List_change, na.rm = TRUE),
    median = median(List_change, na.rm = TRUE),
    IQR = IQR(List_change, na.rm = TRUE)
  )
print(summary_stats)

##Design recovery according to ASM
summary_stats_design <- clinical_info_filtered %>%
  group_by(ASM_nbr) %>%
  summarise(
    count = n(),
    mean = mean(Design_change, na.rm = TRUE),
    sd = sd(Design_change, na.rm = TRUE),
    median = median(Design_change, na.rm = TRUE),
    IQR = IQR(Design_change, na.rm = TRUE)
  )
print(summary_stats_design)
```
# ASM - Permutation test: 
```{r}
# Load the necessary package
if(!require(coin)) install.packages("coin", dependencies=TRUE)
library(coin)

## Permutation tests: All TLE
#List recovery
perm_test <- oneway_test(clinical_info$List_change ~ clinical_info$ASM_nbr, distribution = "exact")
print(perm_test)
#Z = -0.86549, p-value = 0.3995
#Design recovery
perm_test <- oneway_test(clinical_info_filtered$Design_change ~ clinical_info_filtered$ASM_nbr, distribution = "exact")
print(perm_test)
#Z = 2.078, p-value = 0.036
```
# summary stats: ongoing seizures
```{r}
#LIST RECOVERY
summary_stats <- clinical_info %>%
  group_by(Seizure_Profile) %>%
  summarise(
    count = n(),
    mean = mean(List_change, na.rm = TRUE),
    sd = sd(List_change, na.rm = TRUE),
    median = median(List_change, na.rm = TRUE),
    IQR = IQR(List_change, na.rm = TRUE)
  )
print(summary_stats)

#DESIGN RECOVERY
summary_stats <- clinical_info %>%
  group_by(Seizure_Profile) %>%
  summarise(
    count = n(),
    mean = mean(Design_change, na.rm = TRUE),
    sd = sd(Design_change, na.rm = TRUE),
    median = median(Design_change, na.rm = TRUE),
    IQR = IQR(Design_change, na.rm = TRUE)
  )
print(summary_stats)
```
#Permutation tests: ongoing sz
```{r}
# Permutation tests
perm_test_list_change <- oneway_test(clinical_info$List_change ~ clinical_info$Seizure_Profile, distribution = "exact")
print(perm_test_list_change)
#Z = 0.39264, p-value = 0.7074
perm_test_design_change <- oneway_test(clinical_info$Design_change ~ clinical_info$Seizure_Profile, distribution = "exact")
print(perm_test_design_change)
#Z = 1.4367, p-value = 0.1591
```

# summary stats: HS pathology
```{r}
clinical_info$HS<-factor(clinical_info$HS,c(1,0),labels=c('HS','no_HS'))

#List change:
median <- tapply(clinical_info$List_change, clinical_info$HS, median, na.rm=T) #na.rm=T removes rows with missing values
IQR <- tapply(clinical_info$List_change, clinical_info$HS, IQR, na.rm=T) 
min <-  tapply(clinical_info$List_change, clinical_info$HS, min, na.rm=T)
max <-  tapply(clinical_info$List_change, clinical_info$HS, max, na.rm=T)
summary_HS <- cbind(median, IQR, min, max)
print(summary_HS)

#Design
median_design <- tapply(clinical_info$Design_change, clinical_info$HS, median, na.rm=T)
IQR_design <- tapply(clinical_info$Design_change, clinical_info$HS, IQR, na.rm=T) 
min_design <-  tapply(clinical_info$Design_change, clinical_info$HS, min, na.rm=T)
max_design <-  tapply(clinical_info$Design_change, clinical_info$HS, max, na.rm=T)
summary_HS_design <- cbind(median_design, IQR_design, min_design, max_design)
print(summary_HS_design)
```

#Permutation test: HS and List_10y Design_10y
```{r}
# List vs HS
perm_test_list <- oneway_test(clinical_info$List_10y ~ clinical_info$HS, distribution = "exact")
print(perm_test_list)

# Design change
perm_test_design <- oneway_test(clinical_info$Design_10y ~ clinical_info$HS, distribution = "exact")
print(perm_test_design)
```


# ######################
# PLOTS: Eigenvariates
# #######################
### adjusted for LTLE or RTLE more NC, control for NARTIQ and ASM

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## List recovery, LTLE:  WRem
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r}
library(ggplot2)
# x is change in list from 02 to 03, y is the eigenvariate 

# right ACC 
list_change <- c(-0.916666667, 0.625, -0.208333333, -0.847222222, 1.361111111, 1.285598706, 0.833333333, 1.326388889, -0.361111111, -0.520833333, 2.472222222)

right_acc <- c(-0.636386231, 0.243851367, -0.188759502, 0.220930756, 0.565420292, -0.074129682, 0.131747116, -0.25963826, 0.043829105, 0.019551094, 0.496629771) 

right_PHG <- c(-0.618396688, -0.283801509, -0.325928735, -0.069804724, 0.529478847, 1.021228516, -0.121264318, 0.388916423, -0.457825629, 0.113416605, 0.158735082)

# Create a data frame
data_change <- data.frame(list_change, right_acc, right_PHG)
# Fit the linear model
model_listchange <- lm(list_change ~ right_acc, data = data_change)

### Plot right ACC
# Calculate the correlation coefficient
correlation_coefficient <- cor(right_acc, list_change)
# plot
ggplot(data_change, aes(x = right_acc, y = list_change )) +
  geom_point() +                             
  geom_smooth(method = "lm", se = FALSE,     
              color ="darkcyan") + #"Right_TLE" = "deeppink4" # "lightblue"
  labs(x = "Response at right anterior cingulate cortex",           
       y = "Change in verbal memory") +       
       #title = paste("R = ", round(correlation_coefficient, 2))) +  # Add correlation 
  #scale_x_continuous(limits = c(-0.8, 0.8)) +  
  theme_minimal() +                         
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        panel.background = element_blank(),  
        plot.background = element_blank()) +
annotate("text", x = 0.2, y = 2,           # Adjust x and y for proper placement
         label = paste("R =", round(correlation_coefficient, 2)), 
         size = 3.5, hjust = 0)
#Print the R-squared and beta value
print(paste("R-squared:", r_squared))
print(paste("Beta value:", beta_value))

### Plot right post PHG
# Calculate the correlation coefficient
correlation_coefficient <- cor(right_PHG, list_change)
# plot
ggplot(data_change, aes(x = right_PHG, y = list_change )) +
  geom_point() +                             
  geom_smooth(method = "lm", se = FALSE,     
              color ="darkcyan") + #"Right_TLE" = "deeppink4" # "lightblue"
  labs(x = "Response at right parahippocampus",           
       y = "Change in verbal memory") +       
  theme_minimal() +                         
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        panel.background = element_blank(),  
        plot.background = element_blank()) +
annotate("text", x = 0.5, y = 2.2,           # Adjust x and y for proper placement
         label = paste("R =", round(correlation_coefficient, 2)), 
         size = 3.5, hjust = 0)
```

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## List recovery, RTLE:  WRem
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r}
library(ggplot2)
# x is change in list from 02 to 03, y is the eigenvariate 
# right PHG: 
list_change <- c(-1.354166667, -0.104166667, 0.3125, 0.277777778, 0.208333333, -0.277777778, -0.729166667, 0, 0.555555556, -0.208333333) 
list_change_outl <- c(-1.354166667, -0.104166667, 0.3125, 0.277777778, 0.208333333, -0.277777778, -0.729166667, 0, 0.555555556, -0.208333333, 2.361111111)

right_PHG <- c(-0.096762047, -0.345343726, 0.152620897, 0.732979348, 0.023573718, -0.286620747, 0.168971155, 0.47906939, 0.389377599, -0.092534925) 

right_FFG <- c(-1.173982471, 0.715960703, 1.038544309, 1.907611574, -0.695055601, -1.481557427, -0.036970727, -0.309135168, 0.30093625, 0.660458403, 0.793409923)

# Create a data frame
data_change <- data.frame(list_change, right_PHG)
data_change_outl <- data.frame(list_change_outl, right_FFG)
# Fit the linear model
model_listchange <- lm(list_change ~ right_PHG, data = data_change)
model_listchange_outl <- lm(list_change_outl ~ right_FFG, data = data_change_outl)


### Plot right PHG
# Calculate the correlation coefficient
correlation_coefficient <- cor(right_PHG, list_change)
# plot
ggplot(data_change, aes(x = right_PHG, y = list_change )) +
  geom_point() +                             
  geom_smooth(method = "lm", se = FALSE,     
              color ="deeppink4") + 
  labs(x = "Response at right remnant parahippocampus",           
       y = "Change in verbal memory") +       
       #title = paste("R = ", round(correlation_coefficient, 2))) +  # Add correlation 
  #scale_x_continuous(limits = c(-0.8, 0.8)) +  
  theme_minimal() +                         
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        panel.background = element_blank(),  
        plot.background = element_blank()) +
annotate("text", x = 0.5, y = -0.5,           # Adjust x and y for proper placement
         label = paste("R =", round(correlation_coefficient, 2)), 
         size = 3.5, hjust = 0)

### Plot right FFG
# Calculate the correlation coefficient
correlation_coefficient <- cor(right_FFG, list_change_outl)
# plot
ggplot(data_change_outl, aes(x = right_FFG, y = list_change_outl )) +
  geom_point() +                             
  geom_smooth(method = "lm", se = FALSE,     
              color ="deeppink4") + 
  labs(x = "Response at right remnant fusiform",           
       y = "Change in verbal memory") +       
       #title = paste("R = ", round(correlation_coefficient, 2))) +  # Add correlation 
  #scale_x_continuous(limits = c(-0.8, 0.8)) +  
  theme_minimal() +                         
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        panel.background = element_blank(),  
        plot.background = element_blank()) +
annotate("text", x = 1.2, y = -0.7,           # Adjust x and y for proper placement
         label = paste("R =", round(correlation_coefficient, 2)), 
         size = 3.5, hjust = 0)
```

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Design recovery, LTLE: FRem
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r}
library(ggplot2)
# left post FFG, ant OFC
design_change <- c(0.771186441, -0.985915493, -0.845070423, 0.895045632, -0.723322989, 1.815713558, -0.338983051, -1.033659585, 1.155801825, 0.192307692, 1.506326092)

left_FFG <- c(0.969214073, 0.149676211, -0.601109016, -0.264984579, 0.311395725, 2.837371804, -0.460032881, -1.003703384, 0.389399412, 0.735881163, 0.808497974) 

right_OFC <- c(0.929589326, -0.51299565, 1.347902042, -0.190216357, 0.290254815, 1.557016074, -0.695275814, -1.171038994, 0.831492878, -0.105082164, 0.243825481) 

# Create a data frame
data_change <- data.frame(design_change, left_FFG, right_OFC)

# Fit the linear model
model_designchange <- lm(design_change ~ left_FFG, data = data_change)
model_designchange_OFC <- lm(design_change ~ right_OFC, data = data_change)

### Plot left_FFG
# Calculate the correlation coefficient
correlation_coefficient <- cor(left_FFG, design_change)
# plot
ggplot(data_change, aes(x = left_FFG, y = design_change )) +
  geom_point() +                             
  geom_smooth(method = "lm", se = FALSE,     
              color ="darkcyan") + 
  labs(x = "Response at left remnant fusiform gyrus",           
       y = "Change in visual memory") +       
       #title = paste("R = ", round(correlation_coefficient, 2))) +  # Add correlation 
  #scale_x_continuous(limits = c(-0.8, 0.8)) +  
  theme_minimal() +                         
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        panel.background = element_blank(),  
        plot.background = element_blank()) +
annotate("text", x = 1.8, y = 0.1,           # Adjust x and y for proper placement
         label = paste("R =", round(correlation_coefficient, 2)), 
         size = 3.5, hjust = 0)

### Plot right_OFC
# Calculate the correlation coefficient
correlation_coefficient <- cor(right_OFC, design_change)
# plot
ggplot(data_change, aes(x = right_OFC, y = design_change )) +
  geom_point() +                             
  geom_smooth(method = "lm", se = FALSE,     
              color ="darkcyan") + 
  labs(x = "Response at right anterior OFC",           
       y = "Change in visual memory") +       
       #title = paste("R = ", round(correlation_coefficient, 2))) +  # Add correlation 
  #scale_x_continuous(limits = c(-0.8, 0.8)) +  
  theme_minimal() +                         
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        panel.background = element_blank(),  
        plot.background = element_blank()) +
annotate("text", x = 1, y = 0.1,           # Adjust x and y for proper placement
         label = paste("R =", round(correlation_coefficient, 2)), 
         size = 3.5, hjust = 0)

```

# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
## Design recovery, RTLE: FRem
# ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
```{r}
library(ggplot2)
# left globus pallidus and left FFG
design_change <- c(1.730769231, 1.267605634, -0.508474576, 0.426327194, 2.014800668, -0.704225352, -1.86440678, 1.310575316, 0.332597998, -0.262592504)

left_pallidum <- c(1.558358917, 0.131446139, -0.227860587, 0.598544378, 0.505751863, 0.148465154, -0.326727165, 0.19675164, 0.058104725, -0.007225765) #LHC

right_PHG <- c(2.398616409, 0.565412778, 0.004592713, -0.409128987, 1.123366454, 1.029097785, -0.472683241, 0.299824826, 0.407233751, 0.052716348) #RHC

# Create a data frame
data_change <- data.frame(design_change, left_pallidum, right_PHG)
# Fit the linear model
model_designchange <- lm(design_change ~ left_pallidum, data = data_change)
model_designchange_PHG <- lm(design_change ~ right_PHG, data = data_change)


### Plot left_pallidum
# Calculate the correlation coefficient
correlation_coefficient <- cor(left_pallidum, design_change)
# plot
ggplot(data_change, aes(x = left_pallidum, y = design_change )) +
  geom_point() +                             
  geom_smooth(method = "lm", se = FALSE,     
              color ="deeppink4") + 
  labs(x = "Response at left globus pallidus",           
       y = "Change in visual memory") +       
       #title = paste("R = ", round(correlation_coefficient, 2))) +  # Add correlation 
  #scale_x_continuous(limits = c(-0.8, 0.8)) +  
  theme_minimal() +                         
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        panel.background = element_blank(),  
        plot.background = element_blank()) +
annotate("text", x = 1.2, y = -0.1,           # Adjust x and y for proper placement
         label = paste("R =", round(correlation_coefficient, 2)), 
         size = 3.5, hjust = 0)

### Plot right_PHG
# Calculate the correlation coefficient
correlation_coefficient <- cor(right_PHG, design_change)
# plot
ggplot(data_change, aes(x = right_PHG, y = design_change )) +
  geom_point() +                             
  geom_smooth(method = "lm", se = FALSE,     
              color ="deeppink4") + 
  labs(x = "Response at right remnant parahippocampus",           
       y = "Change in visual memory") +       
       #title = paste("R = ", round(correlation_coefficient, 2))) +  # Add correlation 
  #scale_x_continuous(limits = c(-0.8, 0.8)) +  
  theme_minimal() +                         
  theme(axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),  
        panel.grid.minor = element_blank(),  
        panel.background = element_blank(),  
        plot.background = element_blank()) +
annotate("text", x = 1.8, y = 0,           # Adjust x and y for proper placement
         label = paste("R =", round(correlation_coefficient, 2)), 
         size = 3.5, hjust = 0)
```

# ###########################################   
###  Verbal Memory =  Mean preop, 1y, 10y 
# ###########################################   
```{r}
library(dplyr)
library(ggplot2)

### Process to the PLOT - List 1y and 10y controls, left ATLR, right ATLR :
 # Convert TLE_Group to a factor
demographics$Group <- as.factor(demographics$Group)

# Create a new variable which will have left TLE and Right TLE as groups
list_plot <- demographics
list_plot$Group <- case_when(
  list_plot$Group == 0 ~ "Left ATLR",
  list_plot$Group == 1 ~ "Right ATLR",
  list_plot$Group == 2 ~ "Controls",
  TRUE ~ as.character(list_plot$Group)  # Keep other values unchanged
)

# Check for missing values in List_1y and List_10y
missing_list_1y <- sum(is.na(list_plot$List_1y))
missing_list_10y <- sum(is.na(list_plot$List_10y))

cat("Missing values in List_1y:", missing_list_1y, "\n")
cat("Missing values in List_10y:", missing_list_10y, "\n")

# Impute missing values in List_10y with the median
list_plot$List_10y[is.na(list_plot$List_10y)] <- mean(list_plot$List_10y, na.rm = TRUE)

# 1. Combine List_preop List_1y and List_10y into a single column
list_combined_preop <- list_plot %>%
  pivot_longer(cols = c(List_10y, List_1y, List_preop), names_to = "Variable", values_to = "Value") %>%
  mutate(Variable = factor(Variable, levels = c( "List_preop", "List_1y", "List_10y")))

#2. calculates min_value and max_value for each combination of Group and Variable and then uses these values for the error bars in  plot
 #  min_values and max_values back to list_combined
min_value <- list_combined_preop %>%
  group_by(Group, Variable) %>%
  summarise(min_value = min(Value, na.rm = TRUE))

max_value <- list_combined_preop %>%
  group_by(Group, Variable) %>%
  summarise(max_value = max(Value, na.rm = TRUE))

 # Merge the min_values and max_values back to list_combined
list_combined_preop <- list_combined_preop %>%
  left_join(min_value, by = c("Group", "Variable")) %>%
  left_join(max_value, by = c("Group", "Variable"))

# 3. New column legend_condition based on names inside color_condition, to be used for figure legend
list_combined_preop <- list_combined_preop %>%
mutate(legend_condition = case_when(
  list_combined_preop$Variable == "List_10y" ~ "10 years",
  list_combined_preop$Variable == "List_1y" ~ "3-12 months",
  list_combined_preop$Variable == "List_preop" ~ "before surgery",
  TRUE ~ "stable"
  ))

# PLOT
#Colors of boxplots
custom_colors <- c("Left ATLR" = c("List_preop" = "azure2", "List_1y" = "lightblue", "List_10y" = "darkcyan"),
                   "Right ATLR" = c("List_preop" = "bisque1","List_1y" = "lightpink1", "List_10y" = "deeppink4"),
                   "Controls" = c("List_preop" = "darkgoldenrod1","List_1y" = "darkorange", "List_10y" ="chocolate"))


plot_preop <- ggplot(list_combined_preop, aes(x = Group, y = Value, fill = interaction(Group, Variable))) +
  geom_violin(aes(x = Group, y = Value, fill = interaction(Group, Variable)),
              position = position_dodge(width = 0.9), alpha = 0.6, size = 0) +
  stat_summary(geom = "crossbar",   # To add mean +/- se
               position = position_dodge(NULL),
               width = 0.9, alpha = 0.7) +
  geom_errorbar(aes(ymin = min_value, ymax = max_value),
                position = position_dodge(width = 0.9),
                width = 0.3,                    # Adjust the width of the whiskers
                alpha = 0.7,                    # Adjust transparency
                color = "black") +             # Add black color to whisker lines
  scale_fill_manual(values = custom_colors) +
  labs(x = "Group", y = "Verbal memory z-scores", fill = "Follow-up",
       title = "Verbal memory before, 3-12 months and 10 years after surgery") +
  theme_bw() +
  xlab("") +
  scale_y_continuous(limits = c(-5, 3), breaks = seq(-5, 3, 1)) +
  theme(axis.ticks.length = unit(0.1, "cm")) +
  theme(plot.title = element_text(hjust = 0.5, size = 12, face = "bold"),
        plot.subtitle = element_text(hjust = 0.5, size = 17),
        axis.title.x = element_text(size = 9,  face = "bold"),
        axis.title.y = element_text(size = 9),
        axis.text = element_text(size = 9),
        text = element_text(size = 17))
        #legend.position = "none")  # Remove the legend
        #legend.key.size = unit(2, "lines"))

print(plot_preop)
```

# ##################################
## Visual Memory = Mean Preop, 1y, 10y
# ###########################################   
```{r}
#preprocess data
 # Convert TLE_Group to a factor
demographics$Group <- as.factor(demographics$Group)

# Create a new variable which will have left TLE and Right TLE as groups
design_plot <- demographics
design_plot$Group <- case_when(
  design_plot$Group == 0 ~ "Left ATLR",
  design_plot$Group == 1 ~ "Right ATLR",
  design_plot$Group == 2 ~ "Controls",
  TRUE ~ as.character(design_plot$Group)  # Keep other values unchanged
)

# Check for missing values in Design_1y and Design_10y
missing_design_1y <- sum(is.na(design_plot$Design_1y))
missing_design_10y <- sum(is.na(design_plot$Design_10y))

cat("Missing values in Design_1y:", missing_design_1y, "\n")
cat("Missing values in Design_10y:", missing_design_10y, "\n")

# Impute missing values in Design_10y with the median
design_plot$Design_10y[is.na(design_plot$Design_10y)] <- mean(design_plot$Design_10y, na.rm = TRUE)
design_plot$Design_1y[is.na(design_plot$Design_1y)] <- mean(design_plot$Design_1y, na.rm = TRUE)
design_plot$Design_preop[is.na(design_plot$Design_preop)] <- mean(design_plot$Design_preop, na.rm = TRUE)

```